Tampering Detection In Low-Power Smart Cameras

### 2015-05-27 paper.tex
Messe le ROC nuove

%
%% \subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}
%
%
%\subsection{Performance Assessment}
%\gi{Adriano: Dire come vengono calcolate le ROC curves TPR e FPR, le cifre di merito insomma, spiegando bene che parametro varia}
%
%\gi{Adriano: metti entrambe le ROC curves, affiancate e per bene ed alcuni esempi di sequenze}
\begin{figure}[htb]
\centering
\subfigure[]{\label{fig:ROCdisplacement_luma}\includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement_luma}}
\subfigure[]{\label{fig:ROCdisplacement_fd} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement_fd}}
\caption{ROC curves for displacement detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean luma energy. \textbf{(b)} Analysis of the frame differencing.}
\label{fig:ROCdisplacement}
\end{figure}
\begin{figure}[htb]
\centering
\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
\label{fig:ROCdisplacement}
\label{fig:ROCdefocus}
\end{figure}
Experimental results are shown in Figures \ref{fig:ROCdisplacement} and \ref{fig:ROCdefocus}.
As we could see there is an improvement, in the detection of camera displacements, with our approach which separately analizes the behavior of indicators in adaptive regions.
On the other side, as illustrated in Figure \ref{fig:ROCdefocus}, when monitoring indicators meant to detect blur/defocus, it is more convenient to consider the whole scene at once.
\subsection{Discussion}
\gi{Adriano: Aggiungi qua la complessit\'a computazionale}
% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[tbh]
\centering
\begin{tabular}{l|l|l|l|l|l|l|}
\cline{2-7}
& \multicolumn{3}{l|}{\cellcolor[HTML]{C0C0C0}\textbf{Displacement Detection}}  & \multicolumn{3}{l|}{\cellcolor[HTML]{C0C0C0}\textbf{Defocus Detection}} \\ \cline{2-7} 
& \cellcolor[HTML]{EFEFEF}\textbf{Regions} & \cellcolor[HTML]{EFEFEF}\textbf{Total} & \cellcolor[HTML]{EFEFEF}\textbf{Voronoi} & \cellcolor[HTML]{EFEFEF}\textbf{Regions} & \cellcolor[HTML]{EFEFEF}\textbf{Total} & \cellcolor[HTML]{EFEFEF}\textbf{Voronoi} \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{Luma}}     & 0.9994 & 0.9989 & 0.9985  &            &            &             \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{Gradient}} &  		 &  		  &             & 0.9895 & 0.9996 & 0.9996  \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{FD}}         & 0.9974 & 0.9944 & 0.9974  & 0.5526 & 0.5322 & 0.5391  \\ \hline
\end{tabular}
\caption{Area under curve of the analized solutions}
\label{tab:AUC}
\end{table}

The algorithm uses low computational techniques: the biggest effort is made by computation of the feature $g(t)$, which needs $34$ operations per pixel, due to the Sobel filter used during the convolution.

%Numero di operazioni richieste:
%Calcolo di g(t):
%\begin{itemize}
%\item Norma gradiente: 34 FLOP per pixel
%\item Media delle norme del gradiente
%\end{itemize}
%Calcolo di l(t):
%\begin{itemize}
%\item Media dei valori di grigio
%\item Detrending: 1 FLOP per frame
%\end{itemize}
%Monitoraggio one-shot: 2 confronti
%Monitoraggio sequenziale: 
%Ogni 20 frame
%Calcolo intervalli di confidenza: ~70 FLOP
%Confronto tra intervalli di confidenza: 2 confronti

>>>>

%
%% \subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}
%
%
%\subsection{Performance Assessment}
%\gi{Adriano: Dire come vengono calcolate le ROC curves TPR e FPR, le cifre di merito insomma, spiegando bene che parametro varia}
%
%\gi{Adriano: metti entrambe le ROC curves, affiancate e per bene ed alcuni esempi di sequenze}
\begin{figure}[t]
\centering
\subfigure[]{\label{fig:ROCdisplacement}\includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement}}
\subfigure[]{\label{fig:ROCdefocus} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus}}
\caption{ROC curves for displacement detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean luma energy. \textbf{(b)} Analysis of the frame differencing.}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
Experimental results are shown in Figures \ref{fig:ROCdisplacement} and \ref{fig:ROCdefocus}.
As we could see there is an improvement, in the detection of camera displacements, with our approach which separately analizes the behavior of indicators in adaptive regions.
On the other side, as illustrated in Figure \ref{fig:ROCdefocus}, when monitoring indicators meant to detect blur/defocus, it is more convenient to consider the whole scene at once.
\subsection{Discussion}
\gi{Adriano: Aggiungi qua la complessit\'a computazionale}
% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[tbh]
\centering
\begin{tabular}{l|l|l|l|l|l|l|}
\cline{2-7}
& \multicolumn{3}{l|}{\cellcolor[HTML]{C0C0C0}\textbf{Displacement Detection}}  & \multicolumn{3}{l|}{\cellcolor[HTML]{C0C0C0}\textbf{Defocus Detection}} \\ \cline{2-7} 
& \cellcolor[HTML]{EFEFEF}\textbf{Regions} & \cellcolor[HTML]{EFEFEF}\textbf{Total} & \cellcolor[HTML]{EFEFEF}\textbf{Voronoi} & \cellcolor[HTML]{EFEFEF}\textbf{Regions} & \cellcolor[HTML]{EFEFEF}\textbf{Total} & \cellcolor[HTML]{EFEFEF}\textbf{Voronoi} \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{Luma}}     & 0.9994 & 0.9989 & 0.9985  &            &            &             \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{Gradient}} &  		 &  		  &             & 0.9895 & 0.9996 & 0.9996  \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{FD}}         & 0.9974 & 0.9944 & 0.9974  & 0.5526 & 0.5322 & 0.5391  \\ \hline
\end{tabular}
\caption{Area under curve of the analized solutions}
\label{tab:AUC}
\end{table}

The algorithm uses low computational techniques: the biggest effort is made by computation of the feature $g(t)$, which needs $34$ operations per pixel, due to the Sobel filter used during the convolution.
The computational load could be decreased using Fast Fourier Transform (FFT) \cite{brigham1988fast} and operating in the frequency domain.
%Numero di operazioni richieste:
%Calcolo di g(t):
%\begin{itemize}
%\item Norma gradiente: 34 FLOP per pixel
%\item Media delle norme del gradiente
%\end{itemize}
%Calcolo di l(t):
%\begin{itemize}
%\item Media dei valori di grigio
%\item Detrending: 1 FLOP per frame
%\end{itemize}
%Monitoraggio one-shot: 2 confronti
%Monitoraggio sequenziale: 
%Ogni 20 frame
%Calcolo intervalli di confidenza: ~70 FLOP
%Confronto tra intervalli di confidenza: 2 confronti
